### 2016-02-06 paper.tex
changes in MS-PUF section

In this paper, we show how mixed signal ICs in a device like ADCs and DACs 
have properties that make them amicable for use in PUF applications. By
virtue of having analog components, the PUF properties in these ICs
are significantly more amplified compared to digital PUFs such as those based on
SRAM and ring oscillators. An added advantage is that mixed signal PUFs
have considerably less overheads compared to the contemporary digital PUFs. 
\end{abstract}

@@

\section{Mixed Circuit PUFs}
Nano scale variations in DACs and ADCs.

>>>>

In this paper, we show how mixed signal ICs in a device like ADCs and DACs 
have properties that make them amicable for use as intrinsic PUFs. By
virtue of having analog components, the PUF properties in these ICs
are more stronger compared to digital PUFs such as those based on
SRAM and ring oscillators. An added advantage is that mixed signal PUFs
have considerably less overheads compared to the contemporary digital PUFs. 
\end{abstract}

@@

\section{Mixed Signal PUFs}
This section describes how the MS-PUFs are built.

{\flushleft \em Construction of MS-PUF. }
The MS-PUF is created by connecting an output of a DAC to an
input channel of an ADC. This creates a loop between the processor
core, the DAC, and the ADC as shown in Figure~\ref{fig:ms-puf}.
The sofware generates a challenge in the form of a time-series pattern
comprising of digital values, which are transferred one at a time
to the DAC. Each digital value is converted to an analog voltage or
current and reconverted to a representative digital value by the ADC.
The software program accumulates 
all ADC outputs to form the response to the challenge. Algorithm~\ref{algo:puf_sw}
has the details.

\begin{algorithm}[!ht] \label{algo:puf_sw}
\begin{scriptsize}
	\caption{\emph{Software Program for the MS-PUF}}
	\DontPrintSemicolon
	\KwIn{$\mathbf C$ : an array representing the challenge}
	\KwOut{$\mathbf R$ : an array representing the response}
	\Begin{
		\For{$i \in \{1, 2, \cdots len(\mathbf C)\}$}{
			OutputToDAC($\mathbf C_i$); \\
			/* Wait for ADC to finish conversion */ \;
			$\mathbf R_i$ = InputfromADC(); \;	
		}
		\Return ${\mathbf R}$
	}
\end{scriptsize}
\end{algorithm}

Specify the PUF (formally)

Explain how the analysis is done

Why would we expect to have variation

A DAC output depends on several nano-scale features such 
as variations in voltage references, resistor tolerances, 
capacitive effects, and amplifier differences. This could result 
in two DACs having different responses to the same input. 
Successive approximation ADCs have a in-built DAC, therefore
would be affected by the same variations as the DAC. Additionally,

Better PUFs by considering multiple devices

 could cause two DACs to have different responses

 such as the tolerance

Nano scale variations in DACs and ADCs.
